Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Wording

In \textit{scikit-learn}, we chose a representation of data that is as close as
possible to the matrix representation: datasets are encoded as NumPy
multidimensional arrays for dense data and as SciPy sparse matrices for sparse
data. While those may seem rather unsophisticated data representations
when compared to more object-oriented
constructs, such as those used by Weka~\citep{hall2009weka}. However,
they bring the prime advantage
of allowing us to rely on all NumPy and SciPy vector operations -- often orders
of magnitude faster that the corresponding Python loops -- while allowing us at
the same time to keep the code short and readable. From a practical point of
view, these formats also provide a bunch of data loading and conversion tools
which make them very easy to use in many contexts\footnote{For tasks where the
inputs are text files or semi-structured objects, we provide \textit{vectorizer}
objects that efficiently convert such data to the NumPy or SciPy formats.}.
Finally, this design choice has also been motivated by the fact that, given
their pervasiveness in many other scientific Python packages, many scientific
users of Python are likely to be already familiar with those formats, hence helping
them to familiarize with the project.

>>>>

In \textit{scikit-learn}, we chose a representation of data that is as close as
possible to the matrix representation: datasets are encoded as NumPy
multidimensional arrays for dense data and as SciPy sparse matrices for sparse
data. While those may seem rather unsophisticated data representations
when compared to more object-oriented
constructs, such as those used by Weka~\citep{hall2009weka},
they bring the prime advantage
of allowing us to rely on all NumPy and SciPy vector operations -- often orders
of magnitude faster that the corresponding Python loops -- while allowing us at
the same time to keep the code short and readable. From a practical point of
view, these formats also provide a bunch of data loading and conversion tools
which make them very easy to use in many contexts\footnote{For tasks where the
inputs are text files or semi-structured objects, we provide \textit{vectorizer}
objects that efficiently convert such data to the NumPy or SciPy formats.}.
Finally, this design choice has also been motivated by the fact that, given
their pervasiveness in many other scientific Python packages, many scientific
users of Python are likely to be already familiar with those formats, hence helping
them to familiarize with the project.
